From Real-time Attention Assessment to ``With-me-ness'' in Human-Robot Interaction

### 2015-09-20 paper.tex
Fixed mean, std and times

Six children (ages 5 to 6\fixme{boys? girls?}) were enrolled for this study.
The study took place at school, in a separate room (the computer
lab). The participants were chosen by the teacher, and would come one after the
other for a face-to-face interaction with a {\sc Nao} robot (average duration:
18 min, $SD:$ \fixme{stddev?}).

@@

\fixme{how many rounds for each child?}

Besides, once per interaction, the robot did interrupt the handwriting task to
propose to tell a funny story. The story-telling lasted in average \fixme{how
long?} min, and the turn-based hand-writing task continued afterwards. The
intended purpose of the story-telling episode was to locally trigger a different
set of gaze behaviors.

>>>>

Six children (3 boys and 3 girls with ages 5 to 6) were enrolled for this study.
The study took place at school, in a separate room (the computer
lab). The participants were chosen by the teacher, and would come one after the
other for a face-to-face interaction with a {\sc Nao} robot (the duration has $\mu:
19.59$, $SD:1.58$).

@@

In this case, the number of rounds performed by each subject ($\mu: 12,16$, $SD:2.61$) 
varies depending on the interaction time, their ability writing and the easiness of use.
The number of rounds has a .

Besides, once per interaction, the robot did interrupt the handwriting task to
propose to tell a funny story. The story-telling lasted for 1 min. 58 sec., 
and the turn-based hand-writing task continued afterwards. The
intended purpose of the story-telling episode was to locally trigger a different
set of gaze behaviors.
